LME-MPM applied to quasi-brittle fracture.

### 2020-10-06 _region_-MacBook Pro de Pedro.tex
Revisión MMP

\begin{table}
  \centering
  \begin{tabular}[]{c c c c c c c}
    \hline
      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
    \hline
Value &    2368    &     102.7    &      5.4     &  141  &   31  &  12 \\
    \hline
  \end{tabular}
  \caption[Mechanical properties of thje concrete]{Mechanical
    properties of the high strenght concrete.}
  \label{tab:concrete-properties}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For the present research, a 2D setting of the experiment has been
adopted. Both the hammer and the concrete beam are explicitly
represented in order to properly capture the impact. Several levels of
discretization were required to assess the objectiveness of the
obtained results. The results here exposed are from a discretization
of 21576 material points and 3943 nodes. To achieve better results, an
unestructured grid layout has been adopted focusing the minimum nodal
spacing, 1.2 mm, in the middle of the beam and in the impact surface
of the hammer. For this simulation, \gls{gamma-lme} was fixed to
1.8, this low value of the regularization parameter smooth high stress
overshots after the impact. Here the stabilization properties of the \acrshort{lme}
described in \cite{Molinos2020} becomes crucial to achieve
non-spurious results. In fact, standard linear element were tested
with unsatisfactory results since grid-crossing occurs in the hammer
head producing non realistic forces.\\

First, the reaction and impact forces are validated against their
experimental counterparts. Since the impact forces applied by the
hammer and the reaction forces at the two supports were experimentally
measured, they are compared with numerical ones in Figure
\ref{fig:Reactions-Forces-impact-test}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-Forces-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Note that the general trend of the impact forces was correctly
captured. Observe that in experimental solution the delay between
impact peak and reactions peak does not agree with the numerical
ones. A feasible explanation to this unexpected result can due to a
over-rigidity in the supports. \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
Despite the observed discrepancies, this is out of the scope of this
document, although future research of authors will overcome this
limitation. Similarly, results of support forces will be more
realistic when modelled by a suitable contact algorithm instead of
avoiding any vertical displacement}.\MMP{Navas {\it et al.}
(2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
of the support in order to obtain accurate results of the reaction
forces. Interesting contact algorithms within the \acrshort{mpm}
methodology are available in the literature
\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}

Finally, longitudinal stress distribution and crack propagation are
depicted in Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
evolution agrees with the results obtained by \cite{Navas_2017_ES}
under the \acrshort{otm} framework. Two additional considerations about
this results are concerning the interpolation technique. On the one hand,
in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
allows unstructured grids. This is a remarkable benefit for this kind
of simulations since the majority of the computational effort is
clearly localised in a tiny region of the domain. On the other
hand, there is the possibility to reduce the shape function support to avoid
a material point in one side of the crack is affected by those in the
other side of the crack. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0005}}
\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0015}}
\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0030}}
\caption{Evolution of the stress tensor magnitude for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-vs-damage-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1300) }

>>>>

\begin{table}
  \centering
  \begin{tabular}[]{c c c c c c c}
    \hline
      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
    \hline
Value &    2368    &     102.7    &      5.4     &  141  &   31  &  12 \\
    \hline
  \end{tabular}
  \caption[Mechanical properties of thje concrete]{Mechanical
    properties of the high strenght concrete.}
  \label{tab:concrete-properties}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For the present research, a 2D setting of the experiment has been
adopted. Both the hammer and the concrete beam are explicitly
represented in order to properly capture the impact. Several levels of
discretisation were required to assess the objectiveness of the
obtained results. The results here exposed are from a discretisation
of 21576 material points and 3943 nodes. To achieve better results, an
unstructured grid layout has been adopted focusing the minimum nodal
spacing, 1.2 mm, in the middle of the beam and in the impact surface
of the hammer. For this simulation, \gls{gamma-lme} was fixed to
1.8, this low value of the regularization parameter smooth high stress
overshots after the impact. Here the stabilization properties of the \acrshort{lme}
described in \cite{Molinos2020} becomes crucial to achieve
non-spurious results. In fact, standard linear element were tested
with unsatisfactory results since grid-crossing occurs in the hammer
head producing non realistic forces.\\

First, the reaction and impact forces are validated against their
experimental counterparts. Since the impact forces applied by the
hammer and the reaction forces at the two supports were experimentally
measured, they are compared with numerical ones in Figure
\ref{fig:Reactions-Forces-impact-test}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
  \centering
  \subfigure[Hammer forces]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}}
  \subfigure[Reactions]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Reactions-Time}}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-Forces-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Note that the general trend of the impact forces was correctly
captured. Observe that in experimental solution the delay between
impact peak and reactions peak does not agree with the numerical
ones. A feasible explanation to this unexpected result can due to a
over-rigidity in the supports. \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
Despite the observed discrepancies, this is out of the scope of this
document, although future research of authors will overcome this
limitation. Similarly, results of support forces will be more
realistic when modelled by a suitable contact algorithm instead of
avoiding any vertical displacement}.\MMP{Navas {\it et al.}
(2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
of the support in order to obtain accurate results of the reaction
forces. Interesting contact algorithms within the \acrshort{mpm}
methodology are available in the literature
\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}

Finally, longitudinal stress distribution and crack propagation are
depicted in Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
evolution agrees with the results obtained by \cite{Navas_2017_ES}
under the \acrshort{otm} framework. Two additional considerations about
this results are concerning the interpolation technique. On the one hand,
in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
allows unstructured grids. This is a remarkable benefit for this kind
of simulations since the majority of the computational effort is
clearly localised in a tiny region of the domain. On the other
hand, there is the possibility to reduce the shape function support to avoid
a material point in one side of the crack is affected by those in the
other side of the crack. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0005}}
\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0015}}
\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0030}}
\caption{Evolution of the stress tensor magnitude [MPa] for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-vs-damage-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Local Variables:
%%% ispell-local-dictionary: "en_GB"
%%% End:

\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1304) }
